---
title: "Task_4"
output: html_document
---
#Tidying Data
###*by Lada Maksimova*

## Downloading packs and data

```{r}
`weather` <- readRDS('C:/Users/Xiaomi/Desktop/R_class/weather.rds')
library(tidyr)
View(weather)
```

## Rearranging the table

```{r}
weather1 <- weather %>%
  gather(key = day, value = val, X1 : X31) %>%
  separate(day, c("x", "day"), sep = 1) %>%
  pivot_wider(names_from  = measure, values_from = val) %>%
  arrange(year, month) %>%
  unite(col = date, year, month, day)
```

## Now let's get rid of some useless columns:

```{r}
weather1$X <- NULL
weather1$x <- NULL
```

### Let's look what do we have by now

```{r}
head(weather1)
tail(weather1)
View(weather1)
```

##Now we shold do something with those NA values

```{r}
tidy_weather <- na.omit(weather1)
```
But something went wrong, and all the observations wanished! I suppose it happened, because in every raw there were at least 1 NA value. Well, let's try another way...
```{r}
tidy_weather <- group_by(weather, date ) %>%
+   summarise(Max.TemperatureF = max(Max.TemperatureF , na.rm = T),
+             Min.TemperatureF = max( Min.TemperatureF , na.rm = T),
+             MeanDew.PointF = max(MeanDew.PointF , na.rm = T),
+             Min.DewpointF = max(Min.DewpointF , na.rm = T) , 
+             Max.Humidity = max(Max.Humidity , na.rm = T),
+             Mean.Humidity = max(Mean.Humidity , na.rm = T),
+             Min.Humidity = max(Min.Humidity , na.rm = T),
+             Max.Sea.Level.PressureIn = max(Max.Sea.Level.PressureIn , na.rm = T), 
+             Min.Sea.Level.PressureIn = max(Min.Sea.Level.PressureIn , na.rm = T),
+             Max.VisibilityMiles = max(Max.VisibilityMiles , na.rm = T),
+             Mean.VisibilityMiles = max(Mean.VisibilityMiles , na.rm = T),
+             Min.VisibilityMiles = max(Min.VisibilityMiles , na.rm = T),
+             Max.Wind.SpeedMPH = max(Max.Wind.SpeedMPH , na.rm = T),
+             Mean.Wind.SpeedMPH = max(Mean.Wind.SpeedMPH , na.rm = T),
+             Max.Gust.SpeedMPH = max(Max.Gust.SpeedMPH , na.rm = T),
+             PrecipitationIn = max(PrecipitationIn , na.rm = T),
+             CloudCover = max(CloudCover , na.rm = T),
+             Events = max(Events , na.rm = T),
+             WindDirDegrees = max(WindDirDegrees , na.rm = T))

tidy_weather <- na.omit(tidy_weather)
```
P.S. I left the order of the "dates" the way it is. But it's not 1 -> 30. 1 is followed by 10, 11 etc.
