---
title: "Task 4. Weather"
output: html_document
---

##Tidying Data

*by Lada Maksimova*

## Downloading packs and data

```{r, message=FALSE}
`weather` <- readRDS('C:/Users/Xiaomi/Desktop/R_class/weather.rds')
library(tidyr)
library(dplyr)
library(tidyverse)
```

## Rearranging the table

```{r, message=FALSE}
weather <- weather[,-1]
weather1 <- weather %>%
  pivot_longer(cols = starts_with("X"), names_to = "day", values_to = "value") %>%
  pivot_wider(names_from = "measure", values_from = "value")
```

## Now let's get rid of NAs:

```{r, echo=FALSE}
weather2 <- na.omit(weather1)
```

#### Let's look what do we have by now

```{r}
head(weather2)
tail(weather2)
```

##Let's organize our table and create new column called "Date"

```{r, message=FALSE}
weather3 <- weather2 %>%
  separate(day, c("x", "day"), sep = 1) %>%
  select(-x) %>% 
  arrange(year, month) %>%
  unite(col = Date, year, month, day)
```

##Fixing data types

Let's see what's going on with data types
```{r, echo=FALSE}
summary(weather3) 
```
We see, that all the columns are charecters now. I think, that we should leave "date" as a charecter, change "events" to factor , and all the rest to numeric. 
```{r, message=FALSE, echo=FALSE}
weather_tidy <- weather3
weather_tidy$Events = as.factor(weather_tidy$Events)
library(magrittr)
weather_tidy[, c(2:21, 23)]  %<>% lapply(function(x) as.numeric(as.character(x)))
```
Let's check the summary one more time
```{r, message=FALSE}
summary(weather_tidy)
```
That's better!

##The end.
